Daily Shelter and Overnight Services Availabilities

### 2024-09-26 paper/paper.qmd
added many hists and diagrams

#switch to table here
```{r}
#| label: fig-occupancyrate-vs-month
#| fig-cap: Shelter Occupancy Rate in 2024 Over the Months
#| echo: false

@@

```
# add summary table of funding capacity here
```{r}
#| label: fig-fundingcapacity-summary
#| fig-cap: Funding Capacities of Toronto Emergency Shelters
#| echo: false

summary(data$funding_capacity)
```

```{r}
#| label: fig-fundingcapacity-histogram
#| fig-cap: Funding Capacities of Toronto Emergency Shelters
#| echo: false

@@

We can see that the number of marriages fluctuates across the years.

>>>>

# check if occupancy rate varies over months
```{r}
#| label: fig-occupancyrate-vs-month
#| fig-cap: Shelter Occupancy Rate in 2024 Over the Months
#| echo: false

@@

# first find num shelters per fsa
```{r}
#| label: fig-fsa-numshelters
#| eval: true
#| tbl-cap: "Number of Unique Shelters vs FSA"
#| echo: false

fsa_shelters <- data %>% select(fsa, location_id) %>% group_by(fsa) %>% 
  summarise(numshelters = n_distinct(location_id))

fsa_shelters <- fsa_shelters[order(fsa_shelters$numshelters, decreasing = TRUE), ]
knitr::kable(top_n(fsa_shelters,5,numshelters), align ="c", col.names= c("FSA", "Number of Shelter Locations"))

```
```{r}
hist(fsa_shelters$numshelters)
```

```{r}
#| label: fig-regionoccupancy
#| fig-cap: Average Bed Occupancy of Shelters Across Different FSA Regions
#| echo: false

region_occupancy <- data %>% select(fsa, occupied_beds) %>% group_by(fsa) %>%
  summarise(mean_occupied = mean(occupied_beds))

hist(region_occupancy$mean_occupied)

```
```{r}
#| label: fig-fundingcapacity-histogram
#| fig-cap: "Funding Capacities of Toronto Emergency Shelters"
#| echo: false

@@

# discuss summary stats of funding capacity in text, can consider to only include top few rows of this table
```{r}
#| label: fig-fsa-fundingcapacity
#| eval: true
#| tbl-cap: "Funding Capacities of Toronto Emergency Shelters"
#| echo: false

funding_means <- data %>% select(fsa, funding_capacity) %>% group_by(fsa) %>% 
  summarise(mean_fundingcap = mean(funding_capacity))

funding_means <- funding_means[order(funding_means$mean_fundingcap, decreasing = TRUE), ]

#knitr::kable(top_n(funding_means,5,mean_fundingcap), align ="c", col.names= c("FSA", "Mean Funding Capacity"))
hist(funding_means$mean_fundingcap)
```

```{r}
#| label: fig-unavailabilities-by-fsa
#| eval: true
#| tbl-cap: "Number of Unavailable Beds/Night At Different FSAs"
#| echo: false

unavailable_beds <- data %>% select(fsa, unavailable_beds) %>% group_by(fsa) %>% 
  summarise(mean_unavailable = mean(unavailable_beds))

unavailable_beds <- unavailable_beds[order(unavailable_beds$mean_unavailable, decreasing = TRUE), ]

knitr::kable(top_n(unavailable_beds,5,unavailable_beds$mean_unavailable), 
             align ="c", col.names= c("FSA", "Average Number of Unavailable Beds"))
#hist(unavailable_beds$mean_unavailable)
```
